PACE Solver Description: OCMu64,\\ a solver for One-sided Crossing Minimization

### 2024-09-20 tex/paper.tex
Minor changes.

    Now $r(X, \bar v) = (2F_{\bar v}(b) - 1)X(m) + (X(r) - X(l))$, and $r(\bar u, X) = (1 -
    2F_{\bar u}(b))X(m) - (X(r) - X(l))$. By choosing the weights $X(r), X(l)$ appropriately, we can make
    these two values equal, so it suffices if their \emph{average} is positive, and indeed
    $${(r(X, \bar v) + r(\bar u, X))/2 = X(m)(F_{\bar v}(b) - F_{\bar u}(b)) > 0}.$$
    This implies $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, and thus
    demonstrates that if one wants to show that $u \b v$, when $u,
    v$ are not strongly fixed, one must consider features of the graph other than $u, v$ and
    their neighbours. In other words, \cref{lem:sfp} is optimal. Note that this remark also
    applies in the unweighted case, by taking $l, m, r$ to be sets of nodes rather than
    weighted single nodes.
\end{remark}

@@

\subparagraph{Gluing}
We now turn our attention to \emph{gluing}, i.e., proving that two vertices $u$
and $v$ always go right next to each other, and we can treat them as a single vertex. First,
let us see that we cannot get `strong gluing' result analogous to \cref{lem:sfimplf}.

>>>>

    Now $r(X, \bar v) = (2F_{\bar v}(b) - 1)X(m) + (X(r) - X(l))$, and $r(\bar u, X) = (1 -
    2F_{\bar u}(b))X(m) - (X(r) - X(l))$. By choosing the weights $X(r), X(l)$ appropriately, we can make
    these two values equal, so it suffices if their \emph{average} is positive, and indeed
    $${(r(X, \bar v) + r(\bar u, X))/2 = X(m)(F_{\bar v}(b) - F_{\bar u}(b)) > 0}.$$
    This implies $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, and thus
    demonstrates that if one wants to show that $u \b v$, when $u,
    v$ are not strongly fixed, one must consider features of the graph other than $u, v$ and
    their neighbours. In other words, \cref{lem:sfp} is optimal. Note that this remark also
    applies in the unweighted case, by taking $l, m, r$ to be sets of nodes rather than
    single nodes with weighted edges.
\end{remark}

@@

\subparagraph{Gluing}
We now turn our attention to \emph{gluing}, i.e., proving that two vertices $u$
and $v$ always go right next to each other, and we can treat them as a single vertex. First,
let us see that we cannot get a `strong gluing' result analogous to \cref{lem:sfimplf}.
